\subsection{Variations in Energy Measurements}

In \cite{biksbois} it was found that energy consumption measurements can vary between measurements. This topic is also explored in \cite{Ournani2020}, where the authors discovered that numerous variables affect energy consumption measurements. They conducted experiments on 100 nodes to investigate the impact of controllable parameters and achieved 30 times lower variation.

One such parameter is temperature, which has produced conflicting conclusions. \cite{Kistowski2016} observed energy consumption variation on identical processors, without any correlation between temperature and performance. In contrast, \cite{Wang2018} found the opposite to be true. In \cite{Ournani2020} an experiment was performed, where benchmarks were executed on three different configurations. Right after each other, with a one minute sleep between benchmarks executions and a restart between benchmark executions. The configurations were not found to have an impact on the energy variation. 

\cite{Ournani2020} also examined the effect of C-states on energy variation. Disabling C-states resulted in measurements varying five times less on lower workloads with a 50\% higher energy consumption, while no difference was observed on higher workloads. While \cite{Acun2016} had previously found that disabling Turbo Boost reduced variation from 1\% to 16\%, \cite{Ournani2020} could not find any evidence supporting this.


An experiment in \cite{Ournani2020} explored whether the overhead introduced by Linux and its activities and processes affected energy variation. Disabling non-essential processes, such as Wi-Fi and logging modules, yielded no substantial difference. \cite{Marathe2017, Wang2019} conducted experiments on CPUs of different generations to examine how energy variation differs between them, finding that older CPUs exhibited lower deviation. Although a similar experiment in \cite{Ournani2020} did not confirm that older CPUs always vary less, the authors argued that it depends on the generation and observed that CPUs with lower TDPs deviated less.


%In \cite{biksbois} it was found that when performing energy consumption measurements, the result varies between measurements. This is the topic explored in \cite{Ournani2020}, where they found that measuring energy consumption is affected by a lot of variables. They conducted a set of experiments on 100 nodes in order to investigate the impact of controllable parameters with which they achieved a $30$ times lower variation. One parameter is the temperature, where conflicting conclusions are found. \cite{Kistowski2016} found that energy consumption variation could be observed on identical processors, with no correlation between temperature and performance, while \cite{Wang2018} found the opposite to be true. In \cite{Ournani2020} an experiment was performed, where benchmarks were executed on three different configurations. One configuration executed the benchmarks right after each other, one had a one minute sleep between benchmarks and the last restarted between benchmarks. The effect between the configuration was not found to have an impact on the energy variation. \cite{Ournani2020} also explored the effect C-states had on energy variation, they found that when C-states were disabled measurements varied 5 times less on lower workloads with a $50\%$ higher energy consumption, while on higher workloads no difference was found. \cite{Ournani2020} also looked into the effect of Turbo Boost, as \cite{Acun2016} had previously found disabling this to reduce variation from $1\%$ to $16\%$. \cite{Ournani2020} were however unable to find any evidence of this. An experiment was also conducted in \cite{Ournani2020} to check if the overhead introduced by Linux and its activities and processes had an impact on energy variation. To test this, non-essential processes WIFI and logging modules were disabled, but no substantial difference was observed. In \cite{Marathe2017, Wang2019} experiments were conducted on CPUs of different generations to see how energy variation differs between them, where it was found that older CPUs has a lower deviation. A similar experiment was also conducted in \cite{Ournani2020}, which did not show that older CPUs always vary less. \cite{Ournani2020} argued that it depends on the generation, but do however observe that CPUs with lower TDPs deviates less.