\begin{abstract}
    With the evolution of CPUs over the last years, increasing the number of cores has become the norm resulting in additional resources for software to utilize. Through four research questions, this research investigates the performance gains obtained from the additional processing power and the impact of the P- and E-cores on parallel software. The experiments are conducted on two computers, where the analysis is made based on energy consumption and execution time on a per-core basis and on an increasing number of cores. The experiments are conducted primarily on Windows, where Intel's Running Average Power Limit is unavailable, with Linux as a reference point. The energy consumption on Windows is measured on the best performing measuring instrument, found through a set of experiments when running both micro- and macrobenchmarks, where measurements are compared against a ground truth. Additionally, this work presents a conclusion highlighting the analysis and comparison of the results obtained on Windows and Linux systems. It is found that Windows provides valuable depth to the analysis of energy consumption, whereas Linux is overall found to be the more convenient OS choice due to its minimalist nature with less pre-installed software and background processes. The analysis also showed that the number of measurements taken played a significant role in the confidence level of the results obtained from the experiments. Further research is suggested to increase confidence levels through conducting more measurements and exploring the advantages and disadvantages of representing multiple measurements taken over an extended period as a single value.%, we refer to a ground truth and where the body of knowledge is more extensive in this domain, Linux.

    % In recent years, CPUs have been evolving to have more cores as the standard. This research aims to explore how the added processing power and the P- and E-cores affect parallel software performance through four research questions. The analysis uses benchmarks to measure energy consumption and execution time per core as well as with an increasing number of cores. The experiments are primarily conducted on Windows, where Intel's Running Average Power Limit is not available. To ensure accurate measurement of micro- and macrobenchmarks on Windows, we compare them to the more extensive body of knowledge in this domain on Linux.

    % With the evolution of CPUs over the last few years, increasing the number of cores has become the norm. This research investigates the performance gains obtained from the additional processing power and the impact of the P- and E-cores on parallel software through four research questions.
    % The analysis is conducted using benchmarks, taking into account energy consumption and execution time on a per-core bases and on an increasing number of cores. The experiments conducted in primarily done on Windows, where Intel's Running Average Power Limit is unavailable, with Linux as a reference point. The reference to Linux is made, to compare the performance of measuring instruments made for Windows when running both micro- and macrobenchmarks.
    
    % We compare alternative measurement methods for Windows. The benchmarks in this work include both microbenchmarks and macrobenchmarks.
    % With the evolution of CPUs over the last few years, an increase in the number of cores has become the norm. This work investigates the performance gains obtained from the additional processing power and the impact of the P- and E-cores. Performance is analyzed using benchmarks, considering both energy consumption and execution time on a per-core basis and with an increasing number of cores. As this work is based on Windows, where Intel's Running Average Power Limit is unavailable, we compare alternative measurement methods for Windows. The benchmarks in this work include both microbenchmarks and macrobenchmarks illustrating a more realistic test case.
\end{abstract}