\subsection{Statistical Methods}
The objective of this section is to provide a description of the statistical methods that will be employed in this project. These methods will facilitate the assessment of the validity of our findings and the conclusions derived from the data. In order to achieve this, key statistical techniques have been selected that are appropriate for the context of our study.

\paragraph{Shapiro-Wilk Test}
The Shapiro-Wilk test will be used to examine the normality of the data distribution. This test is chosen due to its ability to effectively determine if the data follows a normal distribution, which is an important assumption for various statistical procedures. Prior research suggests that our data is unlikely to be normally distributed \cite{biksbois}, so it is crucial to verify this assumption using the Shapiro-Wilk test. Understanding the distribution of the data will help inform the choice of subsequent statistical tests.

\paragraph{Mann-Whitney U Test}
Building upon the insights gained from the Shapiro-Wilk test, we will employ non-parametric tests in cases where the data is not normally distributed. To evaluate whether there are statistically significant differences between various measurements, the Mann-Whitney U test will be used. This non-parametric test has been selected due to its capacity to compare two independent samples without assuming normality, providing a robust evaluation of differences between groups.

\paragraph{Cochran's Formula}
In order to determine an appropriate sample size for our research project, we will utilize Cochran's formula. This method is advantageous because it allows for the calculation of an optimal sample size to achieve a desired level of statistical power while minimizing the risk of Type I and Type II errors. The sample size obtained from Cochran's formula will help ensure that our results are both accurate and reliable.

\paragraph{Kendall's Tau Correlation Coefficient}
Finally, to assess the correlations between the measurements and a ground truth, we will use the Kendall's Tau correlation coefficient. This non-parametric measure of association has been chosen because it can effectively evaluate the strength and direction of relationships between ordinal variables, even when the underlying data does not adhere to a normal distribution. Additionally, Kendall's Tau is less sensitive to outliers and skewed data, making it an appropriate choice for our analysis.

In summary, the selection of the Shapiro-Wilk test, Mann-Whitney U test, Cochran's formula, and Kendall's Tau correlation coefficient reflects our commitment to using rigorous and appropriate statistical methods in this research project. These techniques will enable us to draw well-supported conclusions from our data and enhance the overall validity of our findings.