\section{The Database}\label{app:database}

In \cite{biksbois}, a MySQL database was used to store the measurements made by the different measuring instruments. In this work, a similar database will be used, with some modifications made because the focus of this work is different to \cite{biksbois}. The design of the database can be seen in \cref{fig:uml_diagram}, where the \texttt{MeasurementCollection} table defines under what circumstances the measurements were made under. This includes what measuring instrument was used, what test case was running, what DUT the measurements were made on and whether or not there was a burn-in period ect. Compared to \cite{biksbois}, a few extra columns has been added to \texttt{TestCase}, as more focus is on the test cases used in this work, compared to \cite{biksbois}. This includes metadata like compiler, optimizations, and parameters used.


In the \texttt{MeasurementCollection}, the columns \texttt{CollectionNumber} and \texttt{Name} represents what experiment the measurement is from, and the name of the experiment respectively. A column found in both \texttt{MeasurementCollection}, \texttt{Measurement} and \texttt{Sample} is \texttt{AdditionalMetadata}. This column can be used to set values unique for specific rows, where an example could be how some metrics are only measured by one measuring instrument.



The \texttt{Measurement} contains values for the energy consumption during the entire execution time of one test case, while the \texttt{Sample} represents samples taken during the execution of the test case. This means for one row in the \texttt{MeasurementCollection} table, there can exists one to many rows in \texttt{Measurement}. For each row in \texttt{Measurement}, there will be many rows in \texttt{Sample}, where the samples will be a fine grained representation of the measurement.

\input{figures/uml.tex}
