\section{Energy Consumption Over Time}\label{app:timeseries}

This section shows how both macrobenchmarks energy consumption evolves over time for DUT 2, used in \cref{subsec:exp_three}. In this section 3DM and PCM are plottet with two cores and all cores to illustrate the difference the additional resources make. 

3DM can be seen in \cref{fig:exp_3_dut_2_3dm_timeseries_all_cores} and \cref{fig:exp_3_dut_1_3dm_timeseries_two_cores}. In these graphs, the different phases of 3DM can be seen. For both two and ten cores there is a startup period until around $14$ seconds, after which the benchmark starts. On ten cores, load is on $25$ watts for approximately $18$ seconds, while for two cores the energy consumption is on $12$ watts for $60$ seconds. 

\input{tables/experiment-3/3dm-power-over-time.tex}
\input{tables/experiment-3/3dm-power-over-time-2-core.tex}

For PCM, the graphs can be seen in \cref{fig:exp_3_dut_1_pcm_timeseries_all_cores} and \cref{fig:exp_3_dut_1_pcm_timeseries_2_core}. For PCM, a smaller difference can be found between two and ten cores compared to 3DM, and there are a few reasons for this. The load is first of all lower for this benchmark, which means the additional resources gives a diminishing return. When looking at \cref{fig:exp_3_dut_1_pcm_timeseries_2_core} it can however also be observed that the upper limit exceeds what was found for two cores for 3DM, which was $12$ watts. $12$ watts  is exceeded at three points during runtime, this being $230-260$, $390-400$, $580-600$, which amounts to $8\%$ of the total runtime. This indicates that we did not find all background processes related to PCM when setting affinity, resulting in too many resouces being allocated to some processes. An effort was put into finding these processes, but without success. This means that the table in \cref{tab:app-results} represents a lower limit for PCM, as all cores are used for some processes, resulting in a lower execution time and DEC, the results are however still deemed valid.

\input{tables/experiment-3/pcm-power-over-time.tex}
\input{tables/experiment-3/pcm-power-over-time-2-core.tex}