\section{Energy usage trends analysis} \label[subsec]{subsec:trendAnalysis}

Two hypotheses were defined to explore if reactive energy consumption caused DEC consumption to decrease. (\textbf{H1:}) \textit{noise on the electrical network could interfere with the phase synchronization.} This could be due to many machines being connected to the same electrical network and disrupting the harmonics of the network\cite{kullarkar2017power}. The PSU could have generated reactive energy because it was out of phase with the electrical network, where a reduction in noise could help synchronize again. Therefore, the observed changes in energy consumption may be related to the time of the day and week where the measurements were taken, with consumption decreasing when fewer devices were connected to the electrical network during the night and weekends.

\textbf{H2:} \textit{The DUTs' PSUs may be correcting the phase over time with a Power Factor Correction circuit.}  According to \cite{mcdonald2020power}, there were two main types of Power Factor Correction: passive and active. The behavior observed in the results could result from an active Power Factor Correction circuit. In order to explore \textbf{H2}, an email was sent to the manufacturers of both PSUs, to which Cougar did not respond, while Corsair confirmed the PSU had Power Factor Correction but would not give any more details. Therefore we could not determine which type of Power Factor Correction was used.

\input{figures/NightDay}


% In order to confirm or reject the hypotheses made, additional measurements were made during the day and night, to compare if similar trends would be observed. In \cref{subsec:trendAnalysis}, an analysis was conducted where it was found an increasing trend during working hours, and a decreasing trend the rest of the day. The analysis also found the same trend to occur during the weekend, but to a lesser degree, as the energy consumption is lower throughout the day. The same trend was  present on Linux, but generally consumes a bit less energy.(UPDATE WITH LINUX AND DUT1 measurements later)  


% For the second hypothesis, a mail was writing to one of the producers of the power Supplies specifically Corsair in the DUTs for further details. They confirmed that the power supplies did contain some form of PFC, but would not go into more details due to trade secrets. We are unable to determine the exact cause of the changes in energy consumption.

% Previous research in this field, which also utilizes hardware measurements, has not addressed this phenomenon. For example, \cite{georgiou2020energy}, \cite{Koedijk2022diff}, and \cite{khan2018rapl} did not report similar findings, although their studies might have had a similar environmental setting to ours. While these studies are not directly comparable, we would have anticipated some resemblance, indicating that previous research utilizing hardware measurements might not have been extensive enough, as this trend has not been revealed previously to our knowledge.

To explore \textbf{H1} regarding electrical network noise interfering with phase synchronization, measurements were analyzed for both DUTs and OSs over 24 hour periods, where the DUTs executed the same benchmark. The data was then categorized into working hours ($7:00$ to $16:00$) and non-working hours ($16:00$ to $7:00$), where no significant variation in power consumption peaks between the two categories was found. However, periods of low energy usage were higher during \texttt{working hours}, which suggested that they did not affect benchmark measurements but did impact idle case measurements. This observation aligned with the results presented in \cref{fig:evolution_of_medians}, which represent the DEC values. One reason this trend might be easier to see on the idle case is that PSUs are less efficient at low loads, which causes reactive energy to contribute more to overall usage.\cite{PowerSupply} 

\input{figures/NightDayDut1}

The impact of reactive power on low loads was tested by making idle measurements on both DUTs during weekdays and weekends, with the results presented in  \cref{tab:RainBowGraph,tab:RainBowGraph2}. The results showed differences between the energy consumption between working and non-working hours, although minimal. It could also be observed from the results that the same pattern is present during the weekends, but to a lesser degree. It should be noted that the recorded measurements were taken close to the end of a semester, which could influence the results. For DUT2 in \cref{tab:RainBowGraph}, when comparing OSs, Windows had a more considerable difference between peaks and valleys, occurring approximately once every two hours. The reason why these spikes occur is likely scheduling jobs.%, as they were only observed on Windows on DUT2, as DUT1\cref{tab:RainBowGraph2} did not show the same pattern.
Why these peaks only occurred on DUT 2, even with the same version of Windows, is a subject for future work. 

A similar observation of varying energy consumption between working and non-working hours has, to our knowledge, yet to be addressed in existing works\cite{georgiou2020energy,Koedijk2022diff, khan2018rapl}. While these studies were not directly comparable, we anticipated some resemblance, indicating that previous research utilizing hardware measurements might have needed to be more extensive, to reveal this trend.

Through this analysis, it was found that there is a relationship between energy consumption and the time of day. It seemed to be affected by the number of people on the electrical network, as suggested by \textbf{H1}. These observations were made on two DUTs and two OSs over multiple days, showing the same pattern, ideally more measurements would have been made, but due to time constraints it is limited. When comparing day and night, the energy consumption was higher during working hours compared to weekends and nights, but whether the cause is reactive energy or some other unaccounted-for factor is a subject for future work.









%As we observed these effects only during low energy usage periods, we focused on valleys in the time series data by identifying local minimums in each 1-minute window. Analyzing data trends using linear regression, we found that \texttt{working hours} exhibited a slight increase with a slope of 0.633, while \texttt{non-working hours} showed a slight decrease with a slope of -1.288.