\subsection{Experiment Two}\label{subsec:exp_two}

In this second experiment, the best measuring instrument on Windows will be found between those introduced in \cref{subsec:measuring_instruments}, in order to anwer \textbf{RQ2}. The best measuring instrument will be defined as a combination of which measuring instrument will be most correlated with the ground truth, but aspects like ease of use was also considered. Due to some issues with the measuring instrument Scaphandre, the process priority class of the test case was in this experiment set to \texttt{Normal}. Due to an execution of less than a second for \texttt{Mandelbrot} when compiled on Intel's oneApi, \texttt{Mandelbrot}'s parameter will be changed from $16.000$ to $64.000$ which takes the duration of the test case to $\sim 14$ seconds. This is to avoid a case where the Plug only has a single data point when measuring. For this experiment, \texttt{Fannkuch-Redux} will be run for $550$ times, while \texttt{Mandelbrot} will be run for $222$ times, decided based on \cref{tab:initial-measurements}.

\paragraph{Initial Measurements}: Following the initial measurements, Cochran's formula was applied, in order to find how many measurements would be required to gain confidence. This can be found in \cref{app:exp_two_coch}, where for some measuring instruments more measurements were required, and for others there were enough. In cases where there were not enough measurements, the number from Cochran's formula was used to decide how many measurements each measuring instrument needed respectively. When looking at how many measurements are required for each measuring instrument, the Clamp requires the most measurements and will in one case require $44.106$ measurements. Given how much time would be required to do that, a more in depth look was taken into this measuring instrument. In \cref{fig:evolution_of_medians} the evolution of the median, percentiles and whiskers can be seen when plotting from $100-1000$ measurement. For the evolution of the median, it decreases by $3.38\%$ between the median at $100$ measurements and $1000$ measurements, and by $1.02\%$ between $900$ and $1000$ measurements. A pattern can also be observed, where the median decreases as more measurements are made, but given how little the median changes, the argument is made that if Cochran's formula states that more than $1.000$ measurements are required, it will be capped at that.

\input{tables/results/evolution/evolution.tex}

\paragraph{Results:} When analyzing the results, graphs will be shown for the DEC for DUT 1, where additional plots can be found in \cref{app:exp_two}.

\input{tables/results/same-one-api-compiler-different-measuring-instruments-post-update-and-watt/clamp-ipg-lhm-plug-rapl-rapl-scaphandre/mandelbrot/workstationone/intel-one-api/CPU_DEC.tex}
\input{tables/results/same-one-api-compiler-different-measuring-instruments-post-update-and-watt/clamp-ipg-lhm-plug-rapl-rapl-scaphandre/fannkuch-redux/workstationone/intel-one-api/CPU_DEC.tex}






